---
title: "Lab 1-1"
author: "Carl Cunningham"
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
  github_document: default
  html_notebook: default 
always_allow_html: yes
---

## Introduction
This notebook provides a structure for completing the first lab.

## Instructions
Using this notebook, load the file `data/STL_FOOD_Grocery.geojson` into `R`. Then, create a `leaflet` map of your own design that also has a popup providing the name of the grocery store. *Note that I've given you the structure and packages for this week - in future weeks - you'll need to figure this bit out as part of the assignment!*

## Dependencies
This notebook requires the following packages:

```{r load-packages}
# tidyverse packages
library(magrittr)     # pipe operator
library(readr)        # csv tools

# mapping packages
library(mapview)      # preview spatial data
library(leaflet)      # interactive maps
library(sf)           # spatial tools

# other packages
library(here)         # file path management
```

## Load Data
This is my first assignment notebook that involves mapping grocery stores

```{r, load-data}
library(magrittr)     
library(readr)        
library(mapview)      
library(leaflet)      
library(sf)           
library(here)         
```

## Map Grocery Stores
< add your narrative text here >

```{r, map-stores}
grocery <- st_read(here("data", "STL_FOOD_Grocery.geojson"))
```
```{r, map-stores}
leaflet(data = grocery) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addMarkers(popup = ~title)
```
